---
title: "Fars Package"
author: "Jorge Barrera"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Fars Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, echo = FALSE, include = FALSE}
library(farspack)
library(dplyr)
library(maps)
```

This package `farspack` provides functions to access data from the FARS - Fatality Analysis Reporting System- records. According to their webpage "FARS is a nationwide census providing NHTSA, Congress and the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes".

## Functions Implemented

The following functions are available to the user (expored):

- `fars_read()`
- `fars_summarize_years()`
- `fars_map_state()`


## Read Data (`fars_read()`)
Reads files in a given path. Use path as argument
```{r fars_read_example}
filename <- system.file("extdata/accident_2013.csv.bz2", package = "fars")
fars_read(filename)
```

## Summarize Accidents (`fars_summarize_years()`)
Summarize the count of fatalities per mnth per year. use the years of interest as argument.

```{r fars_summarize_years_example}
setwd(system.file("extdata", package = "fars"))
fars_summarize_years(2013:2015)
```


## Accidents Map (`fars_map_state()`)
Plots the location of the accidents. Use the state code and year as arguments.

```{r fars_map_state_example}
setwd(system.file("extdata", package = "fars"))
fars_map_state(45, 2015)
```
